Efficient pedigree recording for fast population genetics simulation

### 2018-01-26 forwards_paper.tex
author summary

>>>>

%%%%%%%%%%%%%%%%%%%%%%
\section*{Author Summary}

Sexually reproducing organisms are related to the others in their species
by the complex web of parent-offspring relationships that constitute the pedigree.
In this paper, we describe a way to record all of these relationships,
as well as how genetic material is passed down through the pedigree,
during a forwards-time population genetic simulation.
To make effective use of this information,
we describe both efficient storage methods for this embellished pedigree
as well as a way to remove all information 
that is irrelevant to the genetic history of a given set of individuals,
which dramatically reduces the required amount of storage space.
Storing this information allows us to produce whole-genome sequence
from simulations of large populations in which we have not explicitly recorded new genomic mutations;
we find that this results in computational run times of up to 50 times faster
than simulations forced to explicitly carry along that information.
